Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-05-12 paper/paper.tex
#15 structure into economics and econometrics

@@

\section{Literature review}

@@

\section{Cities, lineages, and territories}

% #####################################################

\section{Empirical approach}

% #####################################################

\section{Results}

% #####################################################

\section{Validity and robustness}

>>>>

What am I even writing this for?
Who am I writing this for?
What is my role here?

I think it's an interesting question, per se.
When a ruling dynasty goes extinct, what happens to their land?
That is the most interesting way I can phrase this.

What are the most interesting aspects of that, for the purpose of this thesis? Which are the issues I want to discuss?

The details of the empirical strategy which I use to find the answer.

What it says and what it doesn't say.

Explanations \textit{why} there might be an effect, and why it may have the sign it has. Possible channels for this effect to go through.

The economics that are at play. Economic mechanisms, decision makers, markets, costs, benefits, institutions, incentives, strategic behaviour.

I think these are really good already.
Note that "historical context" is not on the list.
That's something to spend one to two paragraphs on.

No, the way to make this interesting is to go really deep into a) the economics and b) the econometrics.

Make me care.
Make the reader care. That's your challenge.

@@

\section{The Economics}

@@

\section{The Econometrics}
